\chapter{Abstract}
Creating immersive 3D environments for virtual reality (VR) experiences presents new design opportunities and challenges that does not appear when creating experiences on a screen. Creating immersive prototypes and exploring concepts in VR is today limited to those with previous knowledge in 3D application development, and testing immersive experiences requires the usage of a HMD, which forces professionals to switch medium from the computer to a HMD. With new advances in this field, there has to be new solutions to these problems. The goal of this thesis is to explore how VR technology can be utilized in the experience design process of VR experiences. Furthermore, immersive concepts based on these will be presented. To achieve the first goal a literature study and expert interviews were conducted, followed by a hardware evaluation of HMDs. From the interviews a number of issues could be identified that corerlates with the research from the literature study. From these findings two suitable phases in the design process were identified suitable; Concept prototyping and testing/tweaking of a created experience. Based on these phases, lo-fi and hi-fi prototypes were developed for HTC Vive and Google DayDream which were selected based on the hardware evaluation. The prototypes were designed and developed using rapid prototyping and tested using a Wizard of Oz approach. The purpose of the prototypes are to solve some of the issues when designing immersive experiences for HMDs. An interactive testing suite for HTC Vive were developed for testing and evaluation of the final prototype, which verifies the validity of the concept.

Using Virtual Reality as a medium for designing virtual experiences is a promising way of solving current issues within this technological field that are identified in this thesis. Tools for object creation and manipulation will aid professionals when exploring new concepts as well as modifing and testing existing immersive experiences. Futhermore, using a Wizard of Oz approach to test VR prototypes is significantly improves the prototype quality without compromising the user experience in this medium.  
